---
title: "SRT411 Assignment 0"
author: "Damien Ko"
date: "2017-01-31"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## GitHub Account
dk215

## Introduction
An individual assignment to complete 14 "Todo""
exercises in the document "A (very) short
introduction to R".

Additional the following "Todo" has been added:
"The final Todo in the document has a footnote.
Write code that will prove that footnote true".

## Document Used
https://cran.r-project.org/doc/contrib/Torfs+Brauer-Short-R-Intro.pdf

## ToDo 1
Compute the difference between 2014 and the
year you started at this university and divide
this by the difference between 2014 and the year
you were born. Multiply this with 100 to get
the percentage of your life you have spent at
this university. Use brackets if you need them
```{r ToDo1}
((2017-2015)/(2017-1997))*100
```

## ToDo 2
Repeat the previous ToDo, but with several
steps in between. You can give the variables
any name you want, but the name has to start
with a letter.
```{r ToDo2}
c=2017
s=2015
b=1997
p=100
((c-s)/(c-b))*p
```

## ToDo 3
Compute the sum of 4, 5, 8 and 11 by first combining them into a vector and then using the
function sum.
```{r ToDo3}
s=c(4,5,8,11)
sum(s)
```

## ToDo 4
Plot 100 normal random numbers.
```{r ToDo4}
x=rnorm(100)
plot(x)
```

## ToDo 5
Find help for the sqrt function.
```{r ToDo5}
help(sqrt)
```

## ToDo 6
Make a file called firstscript.R containing Rcode that generates 100 random numbers and
plots them, and run this script several times
```{r ToDo6}
for (i in 1:3){
  source("firstscript.R")
}
```

## ToDo 7
Put the numbers 31 to 60 in a vector named
P and in a matrix with 6 rows and 5 columns
named Q. Tip: use the function seq. Look at
the different ways scalars, vectors and matrices
are denoted in the workspace window.
```{r ToDo7}
P=c(31:60)
Q=matrix(P,nrow=6,ncol=5)
Q
```

## ToDo 8
Make a script file which constructs three random normal vectors of length 100. Call these
vectors x1, x2 and x3. Make a data frame called
t with three columns (called a, b and c) containing respectively x1, x1+x2 and x1+x2+x3.
Call the following functions for this data frame:
plot(t) and sd(t). Can you understand the
results? Rerun this script a few times.

Note: sd on data.frames has been defunct since R-3.0.0.
```{r ToDo8}
for (i in 1:3){
  source("ToDo8.R")
}
```

## ToDo 9
Add these lines to the script file of the previous
section. Try to find out, either by experimenting or by using the help, what the meaning is of
rgb, the last argument of rgb, lwd, pch, cex.
```{r ToDo9}
source("ToDo9.R")
```

### Meanings
rgb specifies colors of given intensities between 0 to max of the red, green, and blue primaries.

lwd specifies the line width for drawing symbols.

pch specifies the plotting character to use.

cex adjusts the scale of characters or symbols.

## ToDo 10
Make a file called tst1.txt in Notepad from
the example in Figure 4 and store it in your
working directory. Write a script to read it, to
multiply the column called g by 5 and to store
it as tst2.txt.
```{r ToDo10}
source("ToDo10.R")
```


## ToDo 11
Compute the mean of the square root of a vector of 100 random numbers. What happens?
```{r ToDo11}
v=(rnorm(100))
mean(sqrt(v))
```
### Result
NaN (Not a Number) data type result for representing an undefined or unrepresentable value.

## ToDo 12
Make a graph with on the x-axis: today, Sinterklaas 2014 and your next birthday and on
the y-axis the number of presents you expect on
each of these days. Tip: make two vectors first.
```{r ToDo12}
source("ToDo12.R")
```

## ToDo 13
Make a vector from 1 to 100. Make a for-loop
which runs through the whole vector. Multiply
the elements which are smaller than 5 and larger
than 90 with 10 and the other elements with 0.1.
```{r ToDo13}
v=(1:100)
m=c()
for(i in 1:length(v)){
  if(i<5 | i>90){
    m[i]=v[i]*10
  }else{
    m[i]=v[i]*0.1
  }
}
m

```

## ToDo 14
Write a function for the previous ToDo, so
that you can feed it any vector you like
(as argument). Use a for-loop in the function to do the computation with each element. Use the standard R function length
in the specification of the counter.
```{r ToDo14}
fun1=function(arg1,arg2){
  v=(1:100)
  m=c()
  for(i in v){
    if(i<5 | i>90){
      m[i]=v[i]*arg1
    }else{
      m[i]=v[i]*arg2
    }
  }
  m
}
fun1(arg1=0,arg2=0.5)
```

## Additional
Prove the last foot note true.

Actually, people often use more for-loops than necessary. The ToDo above can be done more easily
and quickly without a for-loop but with regular vector computations.

```{r ToDo15}
fun1=function(arg1,arg2){
  a=(1:4)
  b=(5:90)
  c=(91:100)
  m=c(a*arg1,b*arg2,c*arg1)
  m
}
fun1(arg1=2,arg2=0.5)

```

## Acknowledgements
https://nicercode.github.io/guides/reports/

http://rmarkdown.rstudio.com/

https://www.rstudio.com/wp-content/uploads/2016/03/rmarkdown-cheatsheet-2.0.pdf

https://www.r-bloggers.com/how-to-write-the-first-for-loop-in-r/

https://stackoverflow.com/questions/24058054/standard-deviation-on-dataframe-does-not-work

https://stat.ethz.ch/pipermail/r-announce/2013/000561.html

https://egret.psychol.cam.ac.uk/statistics/R/enteringdata.html

http://www.r-tutor.com/r-introduction/basic-data-types/integer

https://en.wikipedia.org/wiki/NaN

https://wiki.mobilizingcs.org/rstudio/plots

https://rstudio-pubs-static.s3.amazonaws.com/7953_4e3efd5b9415444ca065b1167862c349.html

http://paleocave.sciencesortof.com/2013/03/writing-a-for-loop-in-r/